Implicit yaddayadda

### 2011-08-30 papers/PLDI2012/implicitization.tex
figure pompee du rapport de Julien

\usepackage{amsmath}
\usepackage{dmnatbib}
\usepackage{listings}
\lstset{language=C,basicstyle={\rm\fontfamily{ppl}\selectfont},mathescape=true,numbers=left}
\usepackage{hyperref}

@@

Classical interval analysis on this program yields $\lstinline|x_old| \in [-100000,100000]$. We have transformed the first program into the second, manually pruning out infeasible paths; yet in general the resulting program could be exponentially larger than the first, even though not all feasible paths are needed to compute the invariant. Following recent suggestions \cite{Gawlitza_Monniaux_ESOP11,Monniaux_Gonnord_SAS11}, we avoid this space explosion by keeping the second program implicit and working from the first program, yet simulating the analysis of the second program. Contribution \ref{contr:disjunctive} (\S\ref{sec:disjunctive}) replaces the exponential expansion of disjunctive invariant generation from \citet{DBLP:conf/pldi/GulwaniZ10} by an implicit representation; contribution \ref{contr:guided_multigraph} (\S\ref{sec:guided_multigraph}) recasts the ``guided analysis'' from \citet{DBLP:conf/sas/GopanR07} on an implicit representation of the paths in lieu of the individual transitions.

>>>>

\usepackage{amsmath}
\usepackage{dmnatbib}

\usepackage{listings}
\lstset{language=C,basicstyle={\rm\fontfamily{ppl}\selectfont},mathescape=true,numbers=left}

\usepackage{tikz}
\usetikzlibrary{arrows,automata}

\tikzstyle{state}=[circle,fill=black!25,minimum size=13pt,inner sep=0pt]
\tikzstyle{rstate}=[rectangle,fill=black!25,minimum size=13pt,inner sep=0pt]
\tikzstyle{transition}=[rectangle,semithick,draw=black!75,
  			  minimum size=4mm]
\tikzstyle{transition2}=[transition,rectangle,thick,dashed,
  			  minimum size=4mm]
\tikzstyle{PRstate}=[circle,double,draw,fill=blue!15,minimum size=13pt,inner sep=0pt]
\tikzstyle{polyhedra}=[blue!25,opacity=0.5,pattern=north west lines,pattern
color=blue]
\tikzstyle{line}=[black,thick]

\usepackage{hyperref}

@@

\begin{figure}
\label{fig:multigraph}
\centering
\begin{minipage}[c]{.19\textwidth}
\begin{tikzpicture}[->,>=stealth',auto,node distance=1.1cm,
                    semithick,font=\footnotesize]

	\node[PRstate] (n0) {$p$};
	\node[state] (n1) [below left of=n0] {};
	\node[state] (n2) [below right of=n0] {};
	\node[state] (n3) [below right of=n1] {};
	\node[state] (n4) [below left of=n3] {};
	\node[state] (n5) [below right of=n3] {};
	\node[state] (n6) [below right of=n4] {};
	\node[state] (n7) [below left of=n6] {};
	\node[state] (n8) [below right of=n6] {};
	\node[PRstate] (n9) [below right of=n7] {$q$};

  \path [transition] 
		(n0) edge              node {} (n1);
  \path [transition] 
		(n0) edge              node {} (n2);
  \path [transition] 
		(n1) edge              node {} (n3);
  \path [transition] 
		(n2) edge              node {} (n3);
  \path [transition] 
		(n3) edge              node {} (n4);
  \path [transition] 
		(n3) edge              node {} (n5);
  \path [transition] 
		(n4) edge              node {} (n6);
  \path [transition] 
		(n5) edge              node {} (n6);
  \path [transition] 
		(n6) edge              node {} (n7);
  \path [transition] 
		(n6) edge              node {} (n8);
  \path [transition] 
		(n7) edge              node {} (n9);
  \path [transition] 
		(n8) edge              node {} (n9);
\end{tikzpicture}
\end{minipage} 
$\Longrightarrow$
\begin{minipage}[c]{.19\textwidth}
\begin{tikzpicture}[->,>=stealth',auto,node distance=1.1cm,
                    semithick,font=\footnotesize]

	\node[PRstate] (n0) {$p$};
	\node (n1) [below left of=n0] {};
	\node (n2) [below right of=n0] {};
	\node (n3) [below right of=n1] {};
	\node (n4) [below left of=n3] {};
	\node (n5) [below right of=n3] {};
	\node (n6) [below right of=n4] {};
	\node (n7) [below left of=n6] {};
	\node (n8) [below right of=n6] {};
	\node[PRstate] (n9) [below right of=n7] {$q$};

  \path [transition] 
		(n0) edge  [out=0, in=0]            node {} (n9);
  \path [transition] 
		(n0) edge  [out=180, in=180]        node {} (n9);
  \path [transition] 
		(n0) edge  [out=205, in=155]            node {} (n9);
  \path [transition] 
		(n0) edge  [out=230, in=130]            node {} (n9);
  \path [transition] 
		(n0) edge  [out=255, in=105]            node {} (n9);
  \path [transition] 
		(n0) edge  [out=-25, in=25]            node {} (n9);
  \path [transition] 
		(n0) edge  [out=-50, in=50]            node {} (n9);
  \path [transition] 
		(n0) edge  [out=-75, in=75]            node {} (n9);
\end{tikzpicture}
\end{minipage}
\caption{Expansion of the transition graph into a multigraph.}
\end{figure}

Classical interval analysis on this program yields $\lstinline|x_old| \in [-100000,100000]$. We have transformed the first program into the second, manually pruning out infeasible paths; yet in general the resulting program could be exponentially larger than the first (as in Fig.~\ref{fig:multigraph}), even though not all feasible paths are needed to compute the invariant. Following recent suggestions \cite{Gawlitza_Monniaux_ESOP11,Monniaux_Gonnord_SAS11}, we avoid this space explosion by keeping the second program implicit and working from the first program, yet simulating the analysis of the second program, that is, on a transition multigraph (Fig.~\ref{fig:multigraph}). Contribution \ref{contr:disjunctive} (\S\ref{sec:disjunctive}) replaces the exponential expansion of disjunctive invariant generation from \citet{DBLP:conf/pldi/GulwaniZ10} by an implicit representation; contribution \ref{contr:guided_multigraph} (\S\ref{sec:guided_multigraph}) recasts the ``guided analysis'' from \citet{DBLP:conf/sas/GopanR07} on an implicit representation of the paths in lieu of the individual transitions.
